Test susieI using whole genome, s40.22 samples

### 2020-11-24 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
credible set

>>>>

# L's effect on SuSiE

We run SuSiE on each block with true priors and true prior variances. We tested the difference between using `L=1` and `L=5`. We only did this for the low power setting.

```{r reg functions}
ncs_ncausal <- function(susief, main = "nCSvs.nCausal") {
  dt <- fread(susief, header = T)
  ncausal <- dt[, sum(ifcausal), by=list(b,rn)]
  nCS <- dt[, max(cs_index), by=list(b,rn)]
  plot(jitter(ncausal$V1), jitter(nCS$V1), xlab= "No.causal/block", ylab = "No. credible set/block", main= main)
  return(dt)
}

sumPIP_ncausal <- function(susief, main = "sumPIPvs.nCausal"){
  dt <- fread(susief, header = T)
  ncausal <- dt[, sum(ifcausal), by=list(b,rn)]
  sumpip <- dt[, sum(susie_pip), by=list(b,rn)]
  plot(jitter(ncausal$V1), sumpip$V1, xlab= "No.causal/block", ylab = "Regional sum PIP", main = main)
  return(dt)
}
```
## L=1

Note: the data has been added some noise (both X and Y axes for credible set vs. no.causal, X axis for sum of PIP vs. no.causal) for visualization purposes. 
```{r L=1, fig.width=8, fig.height=4}
tags <- paste(rep(1, each = 5), 1:5, sep = "-")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config11.susieI.txt")
f1 <- caliPIP_plot(susieIfs2, main = "L=1")
f2 <- ncausal_plot(susieIfs2, format = "susie", main = "No. Causal Genes")
gridExtra::grid.arrange(f1, f2, ncol =2)

par(mfrow=c(1,2))
dt <- sumPIP_ncausal(susieIfs2[2], main = "L=1")
dt <-ncs_ncausal(susieIfs2[2], main = "L=1, CS=0.95")
```

* True parameters: gene $\pi_1$, `r g <- nrow(dt[type =="gene" & ifcausal !=0])/ nrow(dt[type =="gene"]);g`, SNP $\pi_1$, `r s <-nrow(dt[type =="SNP" & ifcausal !=0])/ nrow(dt[type =="SNP"]);s`. [enrichment = `r g/s`].
* Average PIP: gene `r g <- mean(dt[type =="gene", susie_pip]);g`, SNP `r s <-mean(dt[type =="SNP", susie_pip]);s` . [enrichment = `r g/s`].
* Proportion in credible set (0.95): gene `r g <-nrow(dt[type =="gene" & cs_index !=0])/ nrow(dt[type =="gene"]);g `, SNP `r s <-nrow(dt[type =="SNP" & cs_index !=0])/ nrow(dt[type =="SNP"]);s`. [enrichment = `r g/s`].

## L=5

Note: the data has been added some noise (both X and Y axes for credible set vs. no.causal, X axis for sum of PIP vs. no.causal) for visualization purposes.

```{r L=5, fig.width=8, fig.height=4}
tags <- paste(rep(1, each = 5), 1:5, sep = "-")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config12.susieI.txt")

f1 <- caliPIP_plot(susieIfs2, main = "L=5")
f2 <- ncausal_plot(susieIfs2, format = "susie", main = "No. Causal Genes")
gridExtra::grid.arrange(f1, f2, ncol =2)

par(mfrow=c(1,3))
dt <- sumPIP_ncausal(susieIfs2[2], main = "L=5")
dt <- ncs_ncausal(susieIfs2[2], main = "L=5, CS=0.95")

susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config13.susieI.txt")
dt2 <- ncs_ncausal(susieIfs2[2], main = "L=5, CS=0.8")
```

* True parameters: gene $\pi_1$, `r g <- nrow(dt[type =="gene" & ifcausal !=0])/ nrow(dt[type =="gene"]);g`, SNP $\pi_1$, `r s<-nrow(dt[type =="SNP" & ifcausal !=0])/ nrow(dt[type =="SNP"]);s`. [enrichment = `r g/s`].
* Average PIP: gene `r g <- mean(dt[type =="gene", susie_pip]);g`, SNP `r s <-mean(dt[type =="SNP", susie_pip]);s` . [enrichment = `r g/s`].
* Proportion in credible set (0.95): gene `r g <-nrow(dt[type =="gene" & cs_index !=0])/ nrow(dt[type =="gene"]);g `, SNP `r s <-nrow(dt[type =="SNP" & cs_index !=0])/ nrow(dt[type =="SNP"]);s`. [enrichment = `r g/s`].
* Proportion in credible set (0.8): gene `r g <-nrow(dt2[type =="gene" & cs_index !=0])/ nrow(dt2[type =="gene"]);g `, SNP `r s <-nrow(dt2[type =="SNP" & cs_index !=0])/ nrow(dt2[type =="SNP"]);s`. [enrichment = `r g/s`].
